Growth model analysis 3spp WB

### 2018-07-31 manuscriptAnalysis/MS_Analysis_3spp_WB.Rmd
add in 3spp projection sim

speciesForProj <- 'bkt'

# get mean on mean length by cohort for the fall yoy sample
obsLenStats <-  
  ddGIn2[[speciesForProj]] %>%
    group_by(cohort,ageInSamples) %>%
    summarise(lenMean = mean(observedLength, na.rm=TRUE),
              lenSD = sd(observedLength, na.rm=TRUE)) %>%
    filter(ageInSamples == 1) %>%
    ungroup() %>%
    summarise(lenMeanMean = mean(lenMean, na.rm=TRUE),
              lenSDMean = sd(lenMean, na.rm=TRUE))

#data for running the simulation
simData <- list(
  nReps = 1000, #num of mcmc iterations to grab
  numInd = 500, # number of individual to simulate
  nOccYOY = 3,
  nOccAdult = 7,
  riverIndex = 1, #Levels: west brook < wb jimmy < wb mitchell < wb obear

  species = speciesForProj,
  meanInit = obsLenStats$lenMeanMean,
  sdInit = obsLenStats$lenSDMean,
  nSamplesAvail = mcmcInfo$nChains * mcmcInfo$nSamples
)

simData <- updateSimData(simData)
nB <- getNBetas()
m <- createMatrices()
indVars <- getIndVars()
sizeMat <- projectSizes(m)

@@

predLen <- array2df(sizeMat, levels = list(iter=1:simData$nReps,ind=1:simData$numInd,occ=1:simData$nOcc), label.x="len")

ggplot(predLen, aes(occ,len, group=ind)) +
  geom_point(aes(color=ind))+
  geom_line(aes(color=ind)) +
  facet_wrap(~iter)

>>>>

#data for running the simulation
simData <- list(
  nReps = 100, #num of mcmc iterations to grab
  numInd = 500 , # number of individual to simulate
  nOccYOY = 3,
  nOccAdult = 7,
  riverIndex = 1 #Levels: west brook < wb jimmy < wb mitchell < wb obear
)

stats3Spp <- anov <- list()

for( speciesForProj in c('bkt','bnt','ats') ){

  # get mean on mean length by cohort for the fall yoy sample
  obsLenStats <-  
    ddGIn2[[speciesForProj]] %>%
      group_by(cohort,ageInSamples) %>%
      summarise(lenMean = mean(observedLength, na.rm=TRUE),
                lenSD = sd(observedLength, na.rm=TRUE)) %>%
      filter(ageInSamples == 1) %>%
      ungroup() %>%
      summarise(lenMeanMean = mean(lenMean, na.rm=TRUE),
                lenSDMean = mean(lenSD, na.rm=TRUE))

  simData$species = speciesForProj
  simData$meanInit = obsLenStats$lenMeanMean
  simData$sdInit = obsLenStats$lenSDMean
  simData$nSamplesAvail = mcmcInfo$nChains * mcmcInfo$nSamples

  simData <- updateSimData(simData)
  nB <- getNBetas()
  m <- createMatrices()

  indVars <- getIndVars()

  startTime <- Sys.time()
  sizeStats <- sizeStats2 <- NULL
  #loop over conditions
  for(testRow in indVars$rowNum){
    sizeMat <- projectSizes(m,simData,testRow)

    sizeStats1 <- summarizeLens(sizeMat,testRow)
    sizeStats <- rbind(sizeStats,sizeStats1[[1]]) #means over individuals (grouped by iter, occ)
    sizeStats2 <- rbind(sizeStats2,sizeStats1[[2]]) #means by occ of means over individuals (grouped by occ)
  }
  endTime <- Sys.time()
  (elapsed <- endTime - startTime)

  stats3Spp[[speciesForProj]] <- list( sizeStats,sizeStats2 )

  anov[[speciesForProj]] <- anova( lm( lenMean ~ temp + flow + bkt + bnt + ats, data = sizeStats %>% filter(occ == (simData$nOccYOY + simData$nOccAdult))) )

}

ggplot(sizeStats, aes())

@@

ggplot(predLen %>% filter(iter %in% 1:10), aes(occ,len, group=ind)) +
  geom_point(aes(color=ind))+
  geom_line(aes(color=ind)) +
  theme(legend.position = 'none')+
  facet_wrap(~iter)
